---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# drawsample

<!-- badges: start -->
<!-- badges: end -->

The goal of drawsample is to sample data with the desired properties.Samples can be drawn by purposive sampling with determining distributional 
conditions, such as deviation from normality (skewness and kurtosis), 
    and sample size in quantitative research studies.

## Installation

You can install the released version of drawsample from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("drawsample")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("atalay-k/drawsample")
```
## Example

### Examples for *`draw_sample()`* 

#### Draw a sample based on Score_1 (from negatively skewed to normal)

```{r example 1}
library(drawsample)
draw_sample(dist=example_data[,c(1,2)],n=200,skew = 0,kurts = 0,
output_name = c("sample", "1"))
```

#### Draw a sample based on Score_2 (from negatively skewed to positively skewed 

```{r example 2}
draw_sample(dist=example_data[,c(1,3)],n=200,skew = 1,kurts = 1,
output_name = c("sample", "2"))
```

#### Draw a sample based on Score_2 (from negatively skewed to positively skewed with replacement

```{r example 3}

draw_sample(dist=example_data[,c(1,3)],n=200,skew = 0.5,kurts = 0.4,
replacement=TRUE,output_name = c("sample", "3"))

```

### examples for *`draw_sample_n()`*

#### Draw a sample based on Score_1 with default values

```{r example 4}
draw_sample_n(dist=example_data[,c(1,2)],n=200,skew = 0,kurts = 0, location=0, delta_var=0,output_name = c("sample", "4"))
```

#### Draw a sample based on Score_2 (location par)

```{r example 5}

draw_sample_n(dist=example_data[,c(1,3)],n=200,skew = 1,kurts = 1,location=-0.5,delta_var=0,output_name = c("sample", "5"))
```

#### Draw a sample based on Score_2 (delta_var par)
```{r example 6}
# Draw a sample based on Score_2 (delta_var par)
draw_sample_n(dist=example_data[,c(1,3)],n=200,skew = 0.5,kurts = 0.4,location=0,delta_var=0.3,output_name = c("sample", "6"))

```


